Sleep, relative to wake, increases both veridical and false memory in the DRM paradigm:

### 2023-07-11 manuscript.Rmd
Test calculation of Cosine in semantic difference analysis
Attempting to attach only the Cosine function from LSAfun
Added opengl libraries required for LSAfun dependency

packagelist <- c('bookdown','knitr','rmarkdown','osfr','plyr','tidyr','dplyr','emmeans','ggplot2','Rmisc','buildmer','lme4','lmerTest','stringr','effects','effectsize','ggdist','car','gridExtra','kableExtra','rstatix','simr','effsize','readr')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

>>>>

# currently activating the LSA package seems to crash the script on github
# now trying a direct call to the Cosine function with the package unactivated

# install.packages("LSAfun")

packagelist <- c('bookdown','knitr','rmarkdown','osfr','plyr','tidyr','dplyr','emmeans','ggplot2','Rmisc','buildmer','lme4','lmerTest','stringr','effects','effectsize','ggdist','car','gridExtra','kableExtra','rstatix','simr','effsize','readr','LSAfun')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))
